%Section: Work Experience at the top
\sectionTitle{Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
  {Present}   {Data Platform Engineer}{NL}{Ahold Delhaize}
  {April 2023} {
    \begin{itemize}
      \item Architected and maintained Terraform modules for scalable infrastructure.
      \item Developed and streamlined CI/CD pipelines for efficient deployment processes.
      \item Designed and developed Python software solutions with Kusto integration for automation and auditing.
      \item Provided crucial cross-team deployment support, fostering collaboration and ensuring successful project rollouts.
      \item Demonstrated leadership in Python project initiatives, ensuring design integrity and quality.
    \end{itemize}
  }
  {Python, Terraform, CI/CD, Azure Kusto, Kubernetes, Azure, DevOps, Git, SQL, Kafka, Prometheus, Grafana, ArgoCD, Docker, Microservices}
  \emptySeparator
  \experience
  {March 2023}   {Data Engineer}{NL}{Ahold Delhaize}
  {March 2022} {
    \begin{itemize}
      \item Big data processing using Azure Databricks and Pyspark
      \item Developed and managed ETL processes, ensuring seamless data transmission to Kafka clusters
      \item Designed monitoring solutions integrated with Prometheus and Grafana for effective performance tracking as a Pyspark Monitoring Architect
      \item Built and maintained robust pipelines for efficient software delivery using GitHub Actions in a secondary focus on CI/CD DevOps engineering
    \end{itemize}
  }
  {Python, Azure, Databricks, Pyspark, DevOps, Git, Terraform, Kubernetes, ArgoCD, SQL, Kafka, Prometheus, Grafana}
  \emptySeparator
  \experience
  {Today}   {Data Engineer}{NL}{Xccelerated, part of Xebia}
  {March 2022} {
    \begin{itemize}
      \item Developed projects aimed at fortifying robust data pipelines, with a focus on unit testing and API development
      \item Leveraged expertise in advanced data technologies such as PySpark, Deep Learning, Kafka, Kubernetes, and GCP to spearhead cutting-edge solutions
      \item Ensured delivery of production-quality Python code, fostering best practices and upholding high standards of code quality
      \item Gained hands-on experience in deploying and maintaining data pipelines and ML models
    \end{itemize}
  }
  {Python, Google Cloud, Redis, Kafka, Microservices, Git, Terraform, Kubernetes, ArgoCD, DBT, SQL, PySpark, Deep Learning}
  \emptySeparator
  \experience
  {March 2022}   {Data Engineer}{NL}{Dashmote}
  {September 2021} {
    \begin{itemize}
      \item Infrastructure as Code (IaC) with Terraform on AWS, including design and implementation of scripts for seamless service deployment.
      \item Maintenance and optimization of legacy Apache Airflow components in Python, ensuring optimal performance.
      \item Deployment, optimization, and development of production-ready Docker images for efficient containerization.
      \item Key achievements include team collaboration and mentorship, design and deployment of a production-ready datalake on AWS, redesign and implementation of CI/CD strategies resulting in faster workflows, maintenance and development of ETL pipeline components.

    \end{itemize}
  }
  {Python, AWS, Docker, DevOps, Airflow, Git, Terraform, Jenkins, SQL, ETL, CI/CD, Athena}
  \emptySeparator
  \experience
  {June 2020}   {Software Developer}{SP}{EY}
  {June 2019} {
    \begin{itemize}
      \item Contributed to software development for automation and ETL tasks using SQL, Python, Java, and Talend.
      \item Managed Linux systems, including Ubuntu and CentOS, ensuring stability and security.
      \item Administered Windows Server environments to maintain optimal performance and reliability.
      \item Executed scripting tasks in Bash and CMD for process automation, alongside involvement in Sage X3 ERP development, full-stack web development, machine learning, data engineering, and business intelligence solutions using SQL and Python.
    \end{itemize}
  }
  {Python, Java, Linux, Machine Learning, SQL, Bash, Windows Server, Talend, ETL, Sage X3, Business Intelligence}
  \emptySeparator
\end{experiences}
